---
title: "Clay Content and Aridity Index"
output: html_notebook
---

```{r}
# Load dataset
suppressWarnings(suppressMessages({
    datacsv <- read_csv("datasets/irrt1vt2_estBD_mar27.csv")
    dataset <- data.frame(datacsv)
}))
```

<b>Note:</b> There are a couple of massive outliers in the dataset, 5 - 10x the change in OC seen in any other study.  Thes rows of data have been removed from the dataset.

```{r}
# Remove outliers
temp_dataset <- split(dataset, dataset$ref_num=="24")
dataset <- temp_dataset$'FALSE'

temp_dataset <- split(dataset, dataset$ref_num=="19")
dataset <- temp_dataset$'FALSE'
```

```{r}
# Factor whole dataset
dataset[sapply(dataset, is.character)] <- lapply(dataset[sapply(dataset, is.character)], as.factor)

# Store rows without N+ and N- pairings in a temporary variable
tempData1a <- split(dataset, dataset$N_pair=="no")
dataseta <- tempData1a$'TRUE'

# For rows that do have a N+ and N- paring, store only the N- rows in a temporary variable
tempData1b <- split(dataset, dataset$N_pair_state=="N+")
datasetb <- tempData1b$'FALSE'

# Combine the two temporary variables into a unified dataset without the N+ treatments where such pairings exist in the dataset
dataset <- rbind(dataseta, datasetb)

# Split Africa dataset by Depth
d <- dataset %>% group_split(depth_cat_2)
d10 <- as.data.frame(d[1])
d20 <- as.data.frame(d[2])
d30 <- as.data.frame(d[3])
d30p <- as.data.frame(d[4])
```

```{r}
# Separate dataset by clay values above and below median clay value
med10 <- median(d10$per_clay_t1, na.rm = TRUE)
med20 <- median(d20$per_clay_t1, na.rm = TRUE)
med30 <- median(d30$per_clay_t1, na.rm = TRUE)
med30p <- median(d30p$per_clay_t1, na.rm = TRUE)


tempD10 <- split(d10, d10$per_clay_t1>=med10)
d10_above_med <- tempD10$'TRUE'
d10_below_med <- tempD10$'FALSE'

tempD20 <- split(d20, d20$per_clay_t1>=med20)
d20_above_med <- tempD20$'TRUE'
d20_below_med <- tempD20$'FALSE'

tempD30 <- split(d30, d30$per_clay_t1>=med30)
d30_above_med <- tempD30$'TRUE'
d30_below_med <- tempD30$'FALSE'

tempD30p <- split(d30p, d30p$per_clay_t1>=med30p)
d30p_above_med <- tempD30p$'TRUE'
d30p_below_med <- tempD30p$'FALSE'


tempD10b <- split(d10, d10$per_clay_t1>="50")
d10_above_50 <- tempD10b$'TRUE'
d10_below_50 <- tempD10b$'FALSE'

tempD20b <- split(d20, d20$per_clay_t1>="50")
d20_above_50 <- tempD20b$'TRUE'
d20_below_50 <- tempD20b$'FALSE'

tempD30b <- split(d30, d30$per_clay_t1>="50")
d30_above_50 <- tempD30b$'TRUE'
d30_below_50 <- tempD30b$'FALSE'

tempD30pb <- split(d30p, d30p$per_clay_t1>="50")
d30p_above_50 <- tempD30pb$'TRUE'
d30p_below_50 <- tempD30pb$'FALSE'
```



# Change Rate 
## 0 - 10 cm 

```{r}
A = data.frame(x = d10_above_50$aridity_index,y=d10_above_50$OC_change_rate)
B = data.frame(x = d10_below_50$aridity_index,y=d10_below_50$OC_change_rate)
ggplot(A,aes(x,y)) + geom_point() + geom_smooth(data=A, method=lm) + geom_point(data=B,colour='red') + geom_smooth(data=B, method=lm) + xlab("Aridity Index") + ylab("OC Change Rate") + ggtitle("Clay Content Separated at 50%")

A = data.frame(x = d10_above_med$aridity_index,y=d10_above_med$OC_change_rate)
B = data.frame(x = d10_below_med$aridity_index,y=d10_below_med$OC_change_rate)
ggplot(A,aes(x,y)) + geom_point() + geom_smooth(data=A, method=lm) + geom_point(data=B,colour='red') + geom_smooth(data=B, method=lm) + xlab("Aridity Index") + ylab("OC Change Rate") + ggtitle("Clay Content Separated at Median Clay Value")
```
<b>Black</b> dots = values <b>above</b> 50%/median value.
<b>Red dots</b> = values <b>below</b> 50%/median value.


## 10 - 20 cm 

```{r}
A = data.frame(x = d20_above_50$aridity_index,y=d20_above_50$OC_change_rate)
B = data.frame(x = d20_below_50$aridity_index,y=d20_below_50$OC_change_rate)
ggplot(A,aes(x,y)) + geom_point() + geom_smooth(data=A, method=lm) + geom_point(data=B,colour='red') + geom_smooth(data=B, method=lm) + xlab("Aridity Index") + ylab("OC Change Rate") + ggtitle("Clay Content Separated at 50%")

A = data.frame(x = d20_above_med$aridity_index,y=d20_above_med$OC_change_rate)
B = data.frame(x = d20_below_med$aridity_index,y=d20_below_med$OC_change_rate)
ggplot(A,aes(x,y)) + geom_point() + geom_smooth(data=A, method=lm) + geom_point(data=B,colour='red') + geom_smooth(data=B, method=lm) + xlab("Aridity Index") + ylab("OC Change Rate") + ggtitle("Clay Content Separated at Median Clay Value")
```
<b>Black</b> dots = values <b>above</b> 50%/median value.
<b>Red dots</b> = values <b>below</b> 50%/median value.


## 20 - 30 cm 

```{r}
A = data.frame(x = d30_above_50$aridity_index,y=d30_above_50$OC_change_rate)
B = data.frame(x = d30_below_50$aridity_index,y=d30_below_50$OC_change_rate)
ggplot(A,aes(x,y)) + geom_point() + geom_smooth(data=A, method=lm) + geom_point(data=B,colour='red') + geom_smooth(data=B, method=lm) + xlab("Aridity Index") + ylab("OC Change Rate") + ggtitle("Clay Content Separated at 50%")

A = data.frame(x = d30_above_med$aridity_index,y=d30_above_med$OC_change_rate)
B = data.frame(x = d30_below_med$aridity_index,y=d30_below_med$OC_change_rate)
ggplot(A,aes(x,y)) + geom_point() + geom_smooth(data=A, method=lm) + geom_point(data=B,colour='red') + geom_smooth(data=B, method=lm) + xlab("Aridity Index") + ylab("OC Change Rate") + ggtitle("Clay Content Separated at Median Clay Value")
```
<b>Black</b> dots = values <b>above</b> 50%/median value.
<b>Red dots</b> = values <b>below</b> 50%/median value.

## 30+ cm 

```{r}
A = data.frame(x = d30p_above_50$aridity_index,y=d30p_above_50$OC_change_rate)
B = data.frame(x = d30p_below_50$aridity_index,y=d30p_below_50$OC_change_rate)
ggplot(A,aes(x,y)) + geom_point() + geom_smooth(data=A, method=lm) + geom_point(data=B,colour='red') + geom_smooth(data=B, method=lm) + xlab("Aridity Index") + ylab("OC Change Rate") + ggtitle("Clay Content Separated at 50%")

A = data.frame(x = d20_above_med$aridity_index,y=d20_above_med$OC_change_rate)
B = data.frame(x = d20_below_med$aridity_index,y=d20_below_med$OC_change_rate)
ggplot(A,aes(x,y)) + geom_point() + geom_smooth(data=A, method=lm) + geom_point(data=B,colour='red') + geom_smooth(data=B, method=lm) + xlab("Aridity Index") + ylab("OC Change Rate") + ggtitle("Clay Content Separated at Median Clay Value")
```
<b>Black</b> dots = values <b>above</b> 50%/median value.
<b>Red dots</b> = values <b>below</b> 50%/median value.