---
title: "Geographical Area OC by Aridity Index"
output:
  html_document:
    df_print: paged
---

```{r}
# Load libraries
suppressWarnings(suppressMessages({
library(tidyverse)
library(ggpubr)
}))
```

```{r}
# Load dataset
suppressWarnings(suppressMessages({
    datacsv <- read_csv("datasets/irrt1vt2_estBD_mar27.csv")
    dataset <- data.frame(datacsv)
}))
```

Removing <b>Lucho-Constantino et al. 2005</b>. This datapoint was enormously different to all other studies, and is statistically an outlier. The OC value changes throughout the course of this study are more than 10x those of any other study. While the study plot for this study is irrigated with wastewater, other studies including wastewater irrigation are still nowhere near this high.


```{r}
# Remove huge outlier
temp_dataset <- split(dataset, dataset$ref_num=="24")
dataset <- temp_dataset$'FALSE'
```


```{r}
# Factor whole dataset
dataset[sapply(dataset, is.character)] <- lapply(dataset[sapply(dataset, is.character)], as.factor)

# Store rows without N+ and N- pairings in a temporary variable
tempData1a <- split(dataset, dataset$N_pair=="no")
dataseta <- tempData1a$'TRUE'

# For rows that do have a N+ and N- paring, store only the N- rows in a temporary variable
tempData1b <- split(dataset, dataset$N_pair_state=="N+")
datasetb <- tempData1b$'FALSE'

# Combine the two temporary variables into a unified dataset without the N+ treatments where such pairings exist in the dataset
dataset <- rbind(dataseta, datasetb)
```

```{r}
# Split dataset by geographical area
X <- dataset %>% group_split(geo_area)
africa <- as.data.frame(X[1])
asia <- as.data.frame(X[2])
europe <- as.data.frame(X[3])
middle_east <- as.data.frame(X[4])
north_america <- as.data.frame(X[5])
oceania <- as.data.frame(X[6])
south_america <- as.data.frame(X[7])
```

```{r}
# Split Africa dataset by Depth
Af_D <- africa %>% group_split(depth_cat_2)
af_d10 <- as.data.frame(Af_D[1])
af_d20 <- as.data.frame(Af_D[2])
af_d30 <- as.data.frame(Af_D[3])
af_d30p <- as.data.frame(Af_D[4])
```

```{r}
# Split Asia dataset by Depth
As_D <- asia %>% group_split(depth_cat_2)
as_d10 <- as.data.frame(As_D[1])
as_d20 <- as.data.frame(As_D[2])
as_d30 <- as.data.frame(As_D[3])
as_d30p <- as.data.frame(As_D[4])
```

```{r}
# Split Europe dataset by Depth
E_D <- europe %>% group_split(depth_cat_2)
e_d10 <- as.data.frame(E_D[1])
e_d20 <- as.data.frame(E_D[2])
e_d30 <- as.data.frame(E_D[3])
e_d30p <- as.data.frame(E_D[4])
```

```{r}
# Split Middle East dataset by Depth
ME_D <- middle_east %>% group_split(depth_cat_2)
me_d10 <- as.data.frame(ME_D[1])
me_d20 <- as.data.frame(ME_D[2])
me_d30 <- as.data.frame(ME_D[3])
me_d30p <- as.data.frame(ME_D[4])
```

```{r}
# Split North America dataset by Depth
NA_D <- north_america %>% group_split(depth_cat_2)
na_d10 <- as.data.frame(NA_D[1])
na_d20 <- as.data.frame(NA_D[2])
na_d30 <- as.data.frame(NA_D[3])
na_d30p <- as.data.frame(NA_D[4])
```

```{r}
# Split Oceania dataset by Depth
O_D <- oceania %>% group_split(depth_cat_2)
o_d10 <- as.data.frame(O_D[1])
o_d20 <- as.data.frame(O_D[2])
o_d30 <- as.data.frame(O_D[3])
o_d30p <- as.data.frame(O_D[4])
```

```{r}
# Split South America dataset by Depth
SA_D <- dataset %>% group_split(depth_cat_2)
sa_d10 <- as.data.frame(SA_D[1])
sa_d20 <- as.data.frame(SA_D[2])
sa_d30 <- as.data.frame(SA_D[3])
sa_d30p <- as.data.frame(SA_D[4])
```


# Africa

```{r}
ggplot(africa, aes(x=aridity_index, y=OC_change_rate)) + geom_point() + geom_smooth(method=lm) + ggtitle("Aridity Index by OC Change Rate - All Depths")
ggplot(af_d10, aes(x=aridity_index, y=OC_change_rate)) + geom_point() + geom_smooth(method=lm) + ggtitle("Aridity Index by OC Change Rate 0 - 10 cm")
ggplot(af_d20, aes(x=aridity_index, y=OC_change_rate)) + geom_point() + geom_smooth(method=lm) + ggtitle("Aridity Index by OC Change Rate 10 - 20 cm")
#ggplot(af_d30, aes(x=aridity_index, y=OC_change_rate)) + geom_point() + geom_smooth(method=lm) + ggtitle("Aridity Index by OC Change Rate") No data at this depth
#ggplot(af_d30p, aes(x=aridity_index, y=OC_change_rate)) + geom_point() + geom_smooth(method=lm) + ggtitle("Aridity Index by OC Change Rate") No data at this depth
```

# Asia

```{r}
ggplot(asia, aes(x=aridity_index, y=OC_change_rate)) + geom_point() + geom_smooth(method=lm) + ggtitle("Aridity Index by OC Change Rate - All Depths")
ggplot(as_d10, aes(x=aridity_index, y=OC_change_rate)) + geom_point() + geom_smooth(method=lm) + ggtitle("Aridity Index by OC Change Rate 0 - 10 cm")
ggplot(as_d20, aes(x=aridity_index, y=OC_change_rate)) + geom_point() + geom_smooth(method=lm) + ggtitle("Aridity Index by OC Change Rate 10 - 20 cm")
ggplot(as_d30, aes(x=aridity_index, y=OC_change_rate)) + geom_point() + geom_smooth(method=lm) + ggtitle("Aridity Index by OC Change Rate 20 - 30 cm")
ggplot(as_d30p, aes(x=aridity_index, y=OC_change_rate)) + geom_point() + geom_smooth(method=lm) + ggtitle("Aridity Index by OC Change Rate 30+ cm")
```

# Europe

```{r}
ggplot(europe, aes(x=aridity_index, y=OC_change_rate)) + geom_point() + geom_smooth(method=lm) + ggtitle("Aridity Index by OC Change Rate - All Depths")
ggplot(e_d10, aes(x=aridity_index, y=OC_change_rate)) + geom_point() + geom_smooth(method=lm) + ggtitle("Aridity Index by OC Change Rate 0 - 10 cm")
ggplot(e_d20, aes(x=aridity_index, y=OC_change_rate)) + geom_point() + geom_smooth(method=lm) + ggtitle("Aridity Index by OC Change Rate 10 - 20 cm")
ggplot(e_d30, aes(x=aridity_index, y=OC_change_rate)) + geom_point() + geom_smooth(method=lm) + ggtitle("Aridity Index by OC Change Rate 20 - 30 cm")
ggplot(e_d30p, aes(x=aridity_index, y=OC_change_rate)) + geom_point() + geom_smooth(method=lm) + ggtitle("Aridity Index by OC Change Rate 30+ cm")
```

# Middle East

```{r}
ggplot(middle_east, aes(x=aridity_index, y=OC_change_rate)) + geom_point() + geom_smooth(method=lm) + ggtitle("Aridity Index by OC Change Rate - All Depths")
ggplot(me_d10, aes(x=aridity_index, y=OC_change_rate)) + geom_point() + geom_smooth(method=lm) + ggtitle("Aridity Index by OC Change Rate 0 - 10 cm")
ggplot(me_d20, aes(x=aridity_index, y=OC_change_rate)) + geom_point() + geom_smooth(method=lm) + ggtitle("Aridity Index by OC Change Rate 10 - 20 cm")
ggplot(me_d30, aes(x=aridity_index, y=OC_change_rate)) + geom_point() + geom_smooth(method=lm) + ggtitle("Aridity Index by OC Change Rate 20 - 30 cm")
ggplot(me_d30p, aes(x=aridity_index, y=OC_change_rate)) + geom_point() + geom_smooth(method=lm) + ggtitle("Aridity Index by OC Change Rate 30+ cm")
```

# North America

```{r}
ggplot(north_america, aes(x=aridity_index, y=OC_change_rate)) + geom_point() + geom_smooth(method=lm) + ggtitle("Aridity Index by OC Change Rate - All Depths")
ggplot(na_d10, aes(x=aridity_index, y=OC_change_rate)) + geom_point() + geom_smooth(method=lm) + ggtitle("Aridity Index by OC Change Rate 0 - 10 cm")
ggplot(na_d20, aes(x=aridity_index, y=OC_change_rate)) + geom_point() + geom_smooth(method=lm) + ggtitle("Aridity Index by OC Change Rate 10 - 20 cm")
ggplot(na_d30, aes(x=aridity_index, y=OC_change_rate)) + geom_point() + geom_smooth(method=lm) + ggtitle("Aridity Index by OC Change Rate 20 - 30 cm")
ggplot(na_d30p, aes(x=aridity_index, y=OC_change_rate)) + geom_point() + geom_smooth(method=lm) + ggtitle("Aridity Index by OC Change Rate 30+ cm")
```

# Oceania

```{r}
ggplot(oceania, aes(x=aridity_index, y=OC_change_rate)) + geom_point() + geom_smooth(method=lm) + ggtitle("Aridity Index by OC Change Rate - All Depths")
ggplot(o_d10, aes(x=aridity_index, y=OC_change_rate)) + geom_point() + geom_smooth(method=lm) + ggtitle("Aridity Index by OC Change Rate 0 - 10 cm")
ggplot(o_d20, aes(x=aridity_index, y=OC_change_rate)) + geom_point() + geom_smooth(method=lm) + ggtitle("Aridity Index by OC Change Rate 10 - 20 cm")
ggplot(o_d30, aes(x=aridity_index, y=OC_change_rate)) + geom_point() + geom_smooth(method=lm) + ggtitle("Aridity Index by OC Change Rate 20 - 30 cm")
#ggplot(o_d30p, aes(x=aridity_index, y=OC_change_rate)) + geom_point() + geom_smooth(method=lm) + ggtitle("Aridity Index by OC Change Rate") No data at this depth
```

# South America

```{r}
ggplot(south_america, aes(x=aridity_index, y=OC_change_rate)) + geom_point() + geom_smooth(method=lm) + ggtitle("Aridity Index by OC Change Rate - All Depths")
ggplot(sa_d10, aes(x=aridity_index, y=OC_change_rate)) + geom_point() + geom_smooth(method=lm) + ggtitle("Aridity Index by OC Change Rate 0 - 10 cm")
ggplot(sa_d20, aes(x=aridity_index, y=OC_change_rate)) + geom_point() + geom_smooth(method=lm) + ggtitle("Aridity Index by OC Change Rate 10 - 20 cm")
ggplot(sa_d30, aes(x=aridity_index, y=OC_change_rate)) + geom_point() + geom_smooth(method=lm) + ggtitle("Aridity Index by OC Change Rate 20 - 30 cm")
ggplot(sa_d30p, aes(x=aridity_index, y=OC_change_rate)) + geom_point() + geom_smooth(method=lm) + ggtitle("Aridity Index by OC Change Rate 30+ cm")
```