---
title: "Irrigation Method by Carbon Change (%)"
output:
  html_document:
    df_print: paged
---

Look for potential differences in Carbon as a percent by irrigation method.

<b>Note:</b> Anywhere an "NA" shows as a category, that means that those are the rows for which there was no irrigation method reported.


```{r}
# Load libraries
suppressWarnings(suppressMessages({
    library(tidyverse)
    library(ggpubr)
}))
```

```{r}
# Load dataset
suppressWarnings(suppressMessages({
    datacsv <- read_csv("datasets/irrt1vt2_estBD_mar27.csv")
    dataset <- data.frame(datacsv)
}))
```

<b>Note:</b> There are a couple of massive outliers in the dataset, 10x the change in OC seen in any other study.  This row of data has been removed from the dataset

```{r}
# Remove outlier
temp_dataset <- split(dataset, dataset$ref_num=="24")
dataset <- temp_dataset$'FALSE'

temp_dataset <- split(dataset, dataset$ref_num=="19")
dataset <- temp_dataset$'FALSE'
```

```{r}
# Factor whole dataset
dataset[sapply(dataset, is.character)] <- lapply(dataset[sapply(dataset, is.character)], as.factor)

# Store rows without N+ and N- pairings in a temporary variable
tempData1a <- split(dataset, dataset$N_pair=="no")
dataseta <- tempData1a$'TRUE'

# For rows that do have a N+ and N- paring, store only the N- rows in a temporary variable
tempData1b <- split(dataset, dataset$N_pair_state=="N+")
datasetb <- tempData1b$'FALSE'

# Combine the two temporary variables into a unified dataset without the N+ treatments where such pairings exist in the dataset
dataset <- rbind(dataseta, datasetb)

# Separate out the 0 - 10 cm depth incrememt
tempData2 <- split(dataset, dataset$depth_cat_2=="0-10cm")
depth_10 <- tempData2$'TRUE'

# Separate out the 10 - 20 cm depth incrememt
tempData2 <- split(dataset, dataset$depth_cat_2=="10-20cm")
depth_20 <- tempData2$'TRUE'

# Separate out the 20 - 30 cm depth incrememt
tempData2 <- split(dataset, dataset$depth_cat_2=="20-30cm")
depth_30 <- tempData2$'TRUE'

# Separate out the 30+ cm depth incrememt
tempData2 <- split(dataset, dataset$depth_cat_2=="30+cm")
depth_30p <- tempData2$'TRUE'
```

```{r}
# function for number of observations 
give.n <- function(x){
  return(c(y = median(x)*1.05, label = length(x))) 
  # experiment with the multiplier to find the perfect position
}

# function for mean labels
mean.n <- function(x){
  return(c(y = median(x)*0.97, label = round(mean(x),2))) 
  # experiment with the multiplier to find the perfect position
}
```


## 0 - 10 cm Depth Increment

```{r}
# Boxplot to visualize the average percent change for each Irrigation Method (Category)
p <- ggboxplot(depth_10, x="irrig_methodcat", y="per_OC_change", 
          #color = "depth_cat_2", palette = c("#00AFBB", "#E7B800", "#71f442", "#fc79e6"),
          ylab = "Organic Carbon Change from T1 to T2 (%)", xlab = "Irrigation Method")
p + stat_summary(fun.data = give.n, geom = "text", fun = median, position = position_nudge(y = 0.5)) + theme(axis.text.x = element_text(angle = 60, hjust = 1))
```

```{r}
# ANOVA and Tukey's for above boxplot
aov_0_10_per_C <- aov(per_OC_change ~ irrig_methodcat, data = depth_10)
summary(aov_0_10_per_C)
plot(aov_0_10_per_C, 2) # View normality of residuals

TukeyHSD(aov_0_10_per_C)
```


## 10 - 20 cm Depth Increment

```{r}
# Boxplot to visualize the average percent change for each Irrigation Method (Category)
p2 <- ggboxplot(depth_20, x="irrig_methodcat", y="per_OC_change", 
          #color = "depth_cat_2", palette = c("#00AFBB", "#E7B800", "#71f442", "#fc79e6"),
          ylab = "Organic Carbon Change from T1 to T2 (%)", xlab = "Irrigation Method")
p2 + stat_summary(fun.data = give.n, geom = "text", fun = median, position = position_nudge(y = 0.5)) + theme(axis.text.x = element_text(angle = 60, hjust = 1))
```

```{r}
# ANOVA and Tukey's for above boxplot
aov_10_20_per_C <- aov(per_OC_change ~ irrig_methodcat, data = depth_20)
summary(aov_10_20_per_C)
plot(aov_10_20_per_C, 2) # View normality of residuals

TukeyHSD(aov_10_20_per_C)
```

## 20 - 30 cm Depth Increment

```{r}
# Boxplot to visualize the average percent change for each Irrigation Method (Category)
p3 <- ggboxplot(depth_30, x="irrig_methodcat", y="per_OC_change", 
          #color = "depth_cat_2", palette = c("#00AFBB", "#E7B800", "#71f442", "#fc79e6"),
          ylab = "Organic Carbon Change from T1 to T2 (%)", xlab = "Irrigation Method")
p3 + stat_summary(fun.data = give.n, geom = "text", fun = median, position = position_nudge(y = 0.5)) + theme(axis.text.x = element_text(angle = 60, hjust = 1))
```

```{r}
# ANOVA and Tukey's for above boxplot
aov_20_30_per_C <- aov(per_OC_change ~ irrig_methodcat, data = depth_30)
summary(aov_20_30_per_C)
plot(aov_20_30_per_C, 2) # View normality of residuals

TukeyHSD(aov_20_30_per_C)
```

## 30+ cm Depth Increment

```{r}
# Boxplot to visualize the average percent change for each Irrigation Method (Category)
p4 <- ggboxplot(depth_30p, x="irrig_methodcat", y="per_OC_change", 
          #color = "depth_cat_2", palette = c("#00AFBB", "#E7B800", "#71f442", "#fc79e6"),
          ylab = "Organic Carbon Change from T1 to T2 (%)", xlab = "Irrigation Method")
p4 + stat_summary(fun.data = give.n, geom = "text", fun = median, position = position_nudge(y = 0.5)) + theme(axis.text.x = element_text(angle = 60, hjust = 1))
```

```{r}
# ANOVA and Tukey's for above boxplot
aov_30p_per_C <- aov(per_OC_change ~ irrig_methodcat, data = depth_30p)
summary(aov_30p_per_C)
plot(aov_30p_per_C, 2) # View normality of residuals

TukeyHSD(aov_30p_per_C)
```

## Percentage Change by Crop type and Depth

```{r}
# Boxplot to visualize the average percent change for each Irrigation Method (Category) and depth
p5 <- ggboxplot(dataset, x="irrig_methodcat", y="per_OC_change", 
          color = "depth_cat_2", palette = c("#00AFBB", "#E7B800", "#71f442", "#fc79e6"),
          ylab = "Organic Carbon Change from T1 to T2 (%)", xlab = "Irrigation Method")
p5 + stat_summary(fun.data = give.n, geom = "text", fun = median, position = position_nudge(y = 0.5)) + theme(axis.text.x = element_text(angle = 60, hjust = 1))
```






