---
title: "OC Change Rate by SOC at Time 1"
output:
  html_document:
    df_print: paged
  html_notebook: default
  pdf_document: default
---

```{r}
# Load libraries
suppressWarnings(suppressMessages({
library(tidyverse)
library(ggpubr)
}))
```

```{r}
# Load dataset
suppressWarnings(suppressMessages({
    datacsv <- read_csv("datasets/irrt1vt2_estBD_mar27.csv")
    dataset <- data.frame(datacsv)
}))
```

Removing <b>Lucho-Constantino et al. 2005</b>. This datapoint was enormously different to all other studies, and is statistically an outlier. The OC value changes throughout the course of this study are more than 10x those of any other study. While the study plot for this study is irrigated with wastewater, other studies including wastewater irrigation are still nowhere near this high.

```{r}
# Remove huge outlier
temp_dataset <- split(dataset, dataset$ref_num=="24")
dataset <- temp_dataset$'FALSE'
```


```{r}
# Factor whole dataset
dataset[sapply(dataset, is.character)] <- lapply(dataset[sapply(dataset, is.character)], as.factor)

# Store rows without N+ and N- pairings in a temporary variable
tempData1a <- split(dataset, dataset$N_pair=="no")
dataseta <- tempData1a$'TRUE'

# For rows that do have a N+ and N- paring, store only the N- rows in a temporary variable
tempData1b <- split(dataset, dataset$N_pair_state=="N+")
datasetb <- tempData1b$'FALSE'

# Combine the two temporary variables into a unified dataset without the N+ treatments where such pairings exist in the dataset
dataset <- rbind(dataseta, datasetb)

# Separate out the 0 - 10 cm depth incrememt
tempData2 <- split(dataset, dataset$depth_cat_2=="0-10cm")
depth_10 <- tempData2$'TRUE'

# Separate out the 10 - 20 cm depth incrememt
tempData2 <- split(dataset, dataset$depth_cat_2=="10-20cm")
depth_20 <- tempData2$'TRUE'

# Separate out the 20 - 30 cm depth incrememt
tempData2 <- split(dataset, dataset$depth_cat_2=="20-30cm")
depth_30 <- tempData2$'TRUE'

# Separate out the 30+ cm depth incrememt
tempData2 <- split(dataset, dataset$depth_cat_2=="30+cm")
depth_30p <- tempData2$'TRUE'
```


## 0 - 10 cm
## Organic Carbon Change Rate by T1 OC

```{r}
ggplot(depth_10, aes(x=organic_C_t1, y=OC_change_rate)) + geom_point() + geom_smooth(method=lm)
```


## 10 - 20 cm
## Organic Carbon Change Rate by T1 OC

```{r}
ggplot(depth_20, aes(x=organic_C_t1, y=OC_change_rate)) + geom_point() + geom_smooth(method=lm)
```


## 20 - 30 cm
## Organic Carbon Change Rate by T1 OC

```{r}
ggplot(depth_30, aes(x=organic_C_t1, y=OC_change_rate)) + geom_point() + geom_smooth(method=lm)
```


## 30+ cm
## Organic Carbon Change Rate by T1 OC

```{r}
ggplot(depth_30p, aes(x=organic_C_t1, y=OC_change_rate)) + geom_point() + geom_smooth(method=lm)
```





